Online {\IterComp}

### 2017-09-16 prof.tex
minor change
Spelling
minor comment
minor changes

\begin{figure}[t]
\centering {
  \includegraphics[scale=0.75]{figs/cfg-example.pdf}\\\vspace{1ex}
  \resizebox{0.45\textwidth}{!}{
  %\scalebox{0.8}{
     \begin{minipage}{0.5\textwidth}
     Instrumented value for each probe $P_i$:
     \begin{align*}
     \omega(P_0) &= w(B_0) + w(B_1) + w(B_4) + w(B_6) + w(B_7) + w(B_8) + w(B_9)\\
     \omega(P_1) &= w(B_2) - w(B_1) - w(B_4) - w(B_6) - w(B_7) - w(B_8)\\
     \omega(P_2) &= w(B_5) - w(B_6)\\
     \omega(P_3) &= w(B_3) - w(B_4) - w(B_6) - w(B_7)
     \end{align*}
     \end{minipage}
  }
}
  \caption{Example of a CFG with its maximum spanning tree in black. Basic blocks and edges highlighted in red are instrumented.
    Instrumenting them is enough for calculating the total work performed by the whole CFG.}
  \label{fig:cfg-example}
\end{figure}

@@

Afterwards, the algorithm propagates the known edge flows, inferring
the symbolic expressions in the unknown edge flows.
This is achieved by performing a bottom-up propagation from the trivially known
edge flows (in red) by applying the Kirchhoff's first law, i.e.,
for each vertex with a single unknown edge flow, we compute the difference between
the known incoming edge flows by the known outgoing edge flows.
Formally,
for each vertex $u\in G$, following a post-order traversal of the spanning tree,
the Kirchhoff's first law is applied as the following symbolic operations:
First, sum all the out-going edge flows
\[
%\Sigma^+_u = \sum_{v\in N^+(u)} D_{(u,v)}
\mathrm{SumOut}(u): \sum_{v\in N^+(u)} D_{(u,v)}
\]
and then sum all the in-coming edge flows
\[
%\Sigma^-_u = \sum_{v\in N^-(u)} D_{(v,u)}
\mathrm{SumIn}(u): \sum_{v\in N^-(u)} D_{(v,u)}
\]
For all out-going neighbor $v\in N^+(u)$,
\[
%\forall v\in N^+(u):  D_{(u,v)} \gets
D_{(u,v)} \gets
\begin{cases}
    D_{(u,v)} & \!\!\!\quad \text{if $D_{(u,v)}\neq 0$}\\
    \mathrm{SumIn}(u) - \mathrm{SumOut}(u)       & \!\!\!\quad \text{otherwise}
\end{cases}
\]
For all in-coming neighbor $v\in N^-(u)$,
\[
%\forall v\in N^-(u):  D_{(v,u)} \gets
D_{(v,u)} \gets
\begin{cases}
    D_{(v,u)} & \!\!\!\quad \text{if $D_{(v,u)}\neq 0$}\\
    \mathrm{SumOut}(u) - \mathrm{SumIn}(u)       & \!\!\!\quad \text{otherwise}
\end{cases}
\]

\paragraph{Composing the aggregated value of the probes:}
If $x$ is a symbolic expression, then $\kappa_P(x)$ represents the coefficient
of the term $P$ in $x$.
In our case, $\kappa_P(x)$ will belong to the set $\{-1,0,1\}$.
Once all the edge flows are known, then, 
for all probes $P$, the amount of work associated
with probe $P$ is:
\[
%\omega(P) = \sum_{u\in G} \kappa_P(\Sigma^+_u)w(u)
\omega(P) = \sum_{u\in G} \kappa_P(\mathrm{SumOut}(u))w(u)
\]

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.75]{figs/cfg-relax-example.pdf}
  \caption{Example of a CFG containing a loop and its decomposition into DAGs.
           The DAGs are the subgraphs within the dashed boundaries.}
  \label{fig:cfg-relax-example}
\end{figure}

>>>>

\begin{figure}[t]
\centering {
  \includegraphics[scale=0.8]{figs/cfg-example.pdf}\\\vspace{1ex}
  \resizebox{0.45\textwidth}{!}{
  %\scalebox{0.8}{
     \begin{minipage}{0.5\textwidth}
     Instrumented value for each probe $P_i$:
     \begin{align*}
     \omega(P_0) &= w(B_0) + w(B_1) + w(B_4) + w(B_6) + w(B_7) + w(B_8) + w(B_9)\\
     \omega(P_1) &= w(B_2) - w(B_1) - w(B_4) - w(B_6) - w(B_7) - w(B_8)\\
     \omega(P_2) &= w(B_5) - w(B_6)\\
     \omega(P_3) &= w(B_3) - w(B_4) - w(B_6) - w(B_7)
     \end{align*}
     \end{minipage}
  }
}
  \caption{Example of a CFG with its maximum spanning tree in black. Basic blocks and edges highlighted in red are instrumented.
    Instrumenting them is enough for calculating the total work performed by the whole CFG.}
  \label{fig:cfg-example}
\end{figure}

@@

Afterwards, the algorithm propagates the known edge flows, inferring
the symbolic expressions in the unknown edge flows.
This is achieved by performing a bottom-up propagation from the trivially known
edge flows (in red) by applying the Kirchhoff's first law, i.e.,
for each vertex with a single unknown edge flow, we compute the difference between
the known incoming edge flows by the known outgoing edge flows.
Formally,
for each vertex $u\in G$, following a post-order traversal of the spanning tree,
the Kirchhoff's first law is applied as the following symbolic operations:
First, sum all the out-going edge flows
\[
%\Sigma^+_u = \sum_{v\in N^+(u)} D_{(u,v)}
\mathrm{SumOut}(u): \sum_{v\in N^+(u)} D_{(u,v)}
\]
and then sum all the in-coming edge flows
\[
%\Sigma^-_u = \sum_{v\in N^-(u)} D_{(v,u)}
\mathrm{SumIn}(u): \sum_{v\in N^-(u)} D_{(v,u)}
\]
For all out-going neighbors $v\in N^+(u)$,
\[
%\forall v\in N^+(u):  D_{(u,v)} \gets
D_{(u,v)} \gets
\begin{cases}
    \mathrm{SumIn}(u) - \mathrm{SumOut}(u) & \!\!\!\quad \text{if $D_{(u,v)} = 0$}\\
    D_{(u,v)}       & \!\!\!\quad \text{otherwise}
\end{cases}
\]
For all in-coming neighbors $v\in N^-(u)$,
\[
%\forall v\in N^-(u):  D_{(v,u)} \gets
D_{(v,u)} \gets
\begin{cases}
    \mathrm{SumOut}(u) - \mathrm{SumIn}(u) & \!\!\!\quad \text{if $D_{(v,u)} = 0$}\\
    D_{(v,u)}  & \!\!\!\quad \text{otherwise}
\end{cases}
\]

\paragraph{Composing the aggregated value of the probes:}
If $x$ is a symbolic expression, then $\kappa_P(x)$ represents the coefficient
of the term $P$ in $x$.
In our case, $\kappa_P(x)$ will belong to the set $\{-1,0,1\}$.
Once all the edge flows are known, then, 
for all probes $P$, the amount of work associated
with probe $P$ is:
\[
%\omega(P) = \sum_{u\in G} \kappa_P(\Sigma^+_u)w(u)
\omega(P) = \sum_{u\in G} \kappa_P(\mathrm{SumOut}(u))w(u)
\]
It would be equally valid to define $\omega(P)$ in terms of $\mathrm{SumIn}(u)$
instead of $\mathrm{SumOut}(u)$,
since these values are equal after populating all edge flows,
as it is enforced by the Kirchhoff's law.

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.8]{figs/cfg-relax-example.pdf}
  \caption{Example of a CFG containing a loop and its decomposition into DAGs.
           The DAGs are the subgraphs within the dashed boundaries.}
  \label{fig:cfg-relax-example}
\end{figure}
